%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Appendix L: Complete Inventory of Tables
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Complete Inventory of Tables}
\label{app:table_inventory}

This appendix argues that a comprehensive table inventory is essential for navigating a dissertation of this scope. With 153 tables distributed across five chapters and eleven appendices, the inventory below enables examiners, practitioners, and future researchers to locate specific evidence, cross-reference findings, and assess the breadth of analytical coverage without sequentially reading all chapters.

Each entry provides the table label (for cross-referencing), full caption, and environment type. Tables are organized by chapter and appendix in order of appearance.

\tablefontsize %% \tablefontsize controls the size centrally for all appendix tables
\sloppy %% Allow flexible line breaking for long label names in narrow columns

%-------------------------------------------------------------------------------
% Chapter 1: Introduction
%-------------------------------------------------------------------------------
\section{Chapter 1: Introduction (14 Tables)}
\label{sec:inv_ch1}

\noindent Table~\ref{tab:inv_ch1_tables} catalogues all 14 tables in Chapter~1 with their labels, captions, and environment types.

\needspace{8\baselineskip}

\tablefontsize
\begin{xltabular}
{\textwidth}{@{} p{0.5cm} L L p{1cm} @{}}
\caption{Inventory of Tables in Chapter 1: Introduction}
\label{tab:inv_ch1_tables} \\
\toprule
\thead{No.} & \thead{Label} & \thead{Caption} & \thead{Type} \\
\midrule
\endfirsthead
\endhead
\midrule
\multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot
1 & tab:problem\_impact & Four Named Problems Motivating This Research & TX \\
2 & tab:stakeholder\_analysis & Stakeholder Analysis: Why the Problem Matters to Decision-Makers & TX \\
3 & tab:research\_objectives & Research Objectives with Method and Chapter Mapping & TX \\
4 & tab:rq\_mapping & Research Questions with Linked Objectives & TX \\
5 & tab:hypotheses & Research Hypotheses with Acceptance Criteria & TX \\
6 & \seqsplit{tab:contribution\_declaration} & Research Contributions and Novelty Declaration & TX \\
7 & tab:non\_claims & What This Study Does Not Claim & TX \\
8 & tab:study\_scope & Study Scope: Five Biomedical Domains & TX \\
9 & tab:study\_boundaries & Study Boundaries with Rationale & TX \\
10 & tab:alignment\_statement & Research Alignment Statement: Problem to Contribution Traceability & TX \\
11 & tab:methodology\_phases & Methodological Phases Overview & TX \\
12 & tab:key\_terms & Definition of Key Terms & TX \\
13 & tab:thesis\_structure & Structure of the Thesis & TX \\
14 & tab:ch1\_quality & Chapter 1 Quality Assessment Matrix & TX \\
\end{xltabular}

\vspace{0.5em}\noindent\textit{Note.} TX = tabularx environment. All Chapter 1 tables use booktabs formatting with \texttt{\textbackslash tablestripes} alternating row shading and \texttt{\textbackslash thead\{\}} navy headers.

%-------------------------------------------------------------------------------
% Chapter 2: Review of Literature
%-------------------------------------------------------------------------------
\section{Chapter 2: Review of Literature (14 Tables)}
\label{sec:inv_ch2}

\noindent Table~\ref{tab:inv_ch2_tables} catalogues all 14 tables in Chapter~2 with their labels, captions, and environment types.

\needspace{8\baselineskip}

\tablefontsize
\begin{xltabular}
{\textwidth}{@{} p{0.5cm} L L p{1cm} @{}}
\caption{Inventory of Tables in Chapter 2: Review of Literature}
\label{tab:inv_ch2_tables} \\
\toprule
\thead{No.} & \thead{Label} & \thead{Caption} & \thead{Type} \\
\midrule
\endfirsthead
\endhead
\midrule
\multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot
1 & tab:search\_strategy & Systematic Literature Search Strategy & TX \\
2 & tab:construct\_summary & Construct Summary Table & TX \\
3 & tab:theory\_construct\_mapping & Theory-to-Construct Mapping & TX \\
4 & tab:theoretical\_foundations & Theoretical Foundations Underpinning the Study & TX \\
5 & tab:who\_prevalence & Global Prevalence and Health Burden Across Study Domains & TX \\
6 & tab:diagnostic\_methods & Current Diagnostic Methods and AI-Based Alternatives by Domain & TX \\
7 & tab:eeg\_biomarkers & EEG Oscillatory Biomarkers by Domain & TX \\
8 & tab:key\_studies & Key Studies and Performance Across Biomedical Domains & TX \\
9 & tab:recent\_advances & Recent Per-Domain Advances in Biomedical AI (2023--2025) & TX \\
10 & tab:existing\_models & Comparison of Existing Models and Frameworks & TX \\
11 & tab:strengths\_limitations & Thematic Strengths and Structural Limitations in Existing Literature & TX \\
12 & tab:research\_gaps & Research Gap Analysis & TX \\
13 & tab:lit\_method\_comparison & Methodological Trends in Prior Research & TX \\
14 & tab:ch2\_quality & Chapter 2 Quality Assessment Matrix & TX \\
\end{xltabular}

\vspace{0.5em}\noindent\textit{Note.} TX = tabularx environment. Chapter 2 tables summarize the systematic literature review across Autism Spectrum Disorder (ASD), including WHO statistics, methodological trends, and gap analysis.

%-------------------------------------------------------------------------------
% Chapter 3: Research Methods
%-------------------------------------------------------------------------------
\section{Chapter 3: Research Methods (16 Tables)}
\label{sec:inv_ch3}

\noindent Table~\ref{tab:inv_ch3_tables} catalogues all 16 tables in Chapter~3 with their labels, captions, and environment types.

\needspace{8\baselineskip}

\tablefontsize
\begin{xltabular}
{\textwidth}{@{} p{0.5cm} L L p{1cm} @{}}
\caption{Inventory of Tables in Chapter 3: Research Methods}
\label{tab:inv_ch3_tables} \\
\toprule
\thead{No.} & \thead{Label} & \thead{Caption} & \thead{Type} \\
\midrule
\endfirsthead
\endhead
\midrule
\multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot
1 & tab:design\_summary & Research Design Summary & TX \\
2 & tab:rq\_traceability & Research Question to Method Traceability Matrix & TX \\
3 & tab:method\_novelty & Standard vs.\ Novel Methodological Components & TX \\
4 & tab:method\_comparison & Methodological Comparison: Typical Single-Domain Studies vs.\ This Study & TX \\
5 & tab:dataset\_chars & Dataset Characteristics Summary & TX \\
6 & tab:data\_sources & Data Source Descriptions and Provenance & TX \\
7 & tab:eeg\_preproc & Eight-Step EEG Preprocessing Pipeline & TX \\
8 & tab:img\_preproc & Five-Step Imaging Preprocessing Pipeline & TX \\
9 & tab:feature\_eng & Feature Engineering Summary Across Seven Categories & TX \\
10 & tab:data\_quality & Data Quality Assurance Matrix & TX \\
11 & \seqsplit{tab:construct\_operationalization} & Construct Operationalization & TX \\
12 & \seqsplit{tab:hypothesis\_test\_alignment} & Hypothesis-to-Test Alignment & TX \\
13 & tab:validity\_framework & Validity and Reliability Framework & TX \\
14 & tab:reliability\_thresholds & Predefined Reliability and Significance Thresholds & TX \\
15 & tab:ethical\_considerations & Ethical Considerations and Mitigation Actions & TX \\
16 & tab:meth\_tradeoffs & Methodological and Data Strategy Trade-offs & TX \\
\end{xltabular}

\vspace{0.5em}\noindent\textit{Note.} TX = tabularx environment. Chapter 3 tables document the Design Science Research methodology, six datasets, preprocessing pipelines, feature engineering, construct operationalization, and validity framework.

%-------------------------------------------------------------------------------
% Chapter 4: Report on Data Analysis and Findings
%-------------------------------------------------------------------------------
\section{Chapter 4: Report on Data Analysis and Findings (18 Tables)}
\label{sec:inv_ch4}

\noindent Table~\ref{tab:inv_ch4_tables} catalogues all 18 tables in Chapter~4 with their labels, captions, and environment types.

\needspace{8\baselineskip}

\tablefontsize
\begin{xltabular}
{\textwidth}{@{} p{0.5cm} L L p{1cm} @{}}
\caption{Inventory of Tables in Chapter 4: Data Analysis and Findings}
\label{tab:inv_ch4_tables} \\
\toprule
\thead{No.} & \thead{Label} & \thead{Caption} & \thead{Type} \\
\midrule
\endfirsthead
\endhead
\midrule
\multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot
1 & tab:data\_screening & Data Screening Summary & TX \\
2 & tab:sample\_profile & Sample Profile and Descriptive Characteristics & TX \\
3 & \seqsplit{tab:classification\_performance} & Classification Performance Across Five Biomedical Domains & TX \\
4 & \seqsplit{tab:confusion\_matrix\_summary} & Confusion Matrix Summary Across Five Biomedical Domains & TX \\
5 & tab:feature\_importance & ASD-Focused Feature Importance (SHAP Analysis) & TX \\
6 & tab:ablation\_study & Ablation Study: Architectural Component Contributions & TX \\
7 & tab:hypothesis\_summary & Hypothesis Testing Summary & TX \\
8 & tab:findings\_rq\_alignment & Findings Aligned to Research Questions & TX \\
9 & tab:evidence\_strength & Evidence Strength Assessment & TX \\
10 & tab:key\_findings\_summary & Key Findings Summary & TX \\
11 & tab:framework\_layers & Five-Layer Framework Architecture & TX \\
12 & tab:decision\_classification & Decision Classification Model & TX \\
13 & tab:governance\_controls & Governance Controls Matrix & TX \\
14 & tab:gap\_framework\_response & Research Gaps and Framework Responses & TX \\
15 & tab:validation\_strategy & Validation Strategy: Four Methods Addressing Distinct Validity Dimensions & TX \\
16 & tab:expert\_review & Expert Panel Validation Results ($n = 12$) & TX \\
17 & tab:scenario\_results & Scenario-Based Application Results Across Five Domains & TX \\
18 & tab:before\_after & Before--After Comparison of Diagnostic Workflow Metrics & TX \\
\end{xltabular}

\vspace{0.5em}\noindent\textit{Note.} TX = tabularx environment. Chapter 4 is the largest chapter by table count, spanning data screening, classification results, framework architecture, governance, and validation outcomes.

%-------------------------------------------------------------------------------
% Chapter 5: Discussion, Recommendations and Areas of Further Research
%-------------------------------------------------------------------------------
\section{Chapter 5: Discussion, Recommendations and Areas of Further Research (10 Tables)}
\label{sec:inv_ch5}

\noindent Table~\ref{tab:inv_ch5_tables} catalogues all 10 tables in Chapter~5 with their labels, captions, and environment types.

\needspace{8\baselineskip}

\tablefontsize
\begin{xltabular}
{\textwidth}{@{} p{0.5cm} L L p{1cm} @{}}
\caption{Inventory of Tables in Chapter 5: Discussion and Recommendations}
\label{tab:inv_ch5_tables} \\
\toprule
\thead{No.} & \thead{Label} & \thead{Caption} & \thead{Type} \\
\midrule
\endfirsthead
\endhead
\midrule
\multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot
1 & tab:findings\_summary & Summary of Hypothesis Testing Outcomes & TX \\
2 & tab:objectives\_achievement & Research Objectives Achievement Summary & TX \\
3 & \seqsplit{tab:theoretical\_contributions} & Theoretical Contributions by Domain & TX \\
4 & tab:literature\_comparison & Findings Compared with Prior Literature & TX \\
5 & tab:research\_contributions & Research Contributions at Three Levels & TX \\
6 & tab:managerial\_implications & Managerial Implications of Key Findings & TX \\
7 & \seqsplit{tab:practical\_recommendations} & Practical Recommendations by Stakeholder and Priority & TX \\
8 & tab:policy\_implications & Policy Implications of Research Findings & TX \\
9 & \seqsplit{tab:contribution\_limitations} & Limitations of Contributions & TX \\
10 & \seqsplit{tab:practitioner\_recommendations} & Practitioner Recommendations by Stakeholder Group & TX \\
\end{xltabular}

\vspace{0.5em}\noindent\textit{Note.} TX = tabularx environment. Chapter 5 tables synthesize findings against hypotheses, compare with prior literature, and present actionable recommendations for practitioners, managers, and policymakers.

%-------------------------------------------------------------------------------
% Summary: Chapter Tables
%-------------------------------------------------------------------------------
\section{Chapter Table Summary}
\label{sec:inv_chapter_summary}

\noindent Table~\ref{tab:inv_chapter_totals} summarises the table counts across all five chapters.
\needspace{8\baselineskip}
{\tablestripes\tablefontsize
\begin{xltabular}{\textwidth}{@{} L C C @{}}
\caption{Summary of Tables Across Five Chapters}\label{tab:inv_chapter_totals} \\
\toprule
\thead{Chapter} & \thead{Table Count} & \thead{Environment} \\
\midrule
\endfirsthead
\multicolumn{3}{@{}l}{\textit{(\,Tab.~\ref{tab:inv_chapter_totals} continued from previous page\,)}} \\
\toprule
\thead{Chapter} & \thead{Table Count} & \thead{Environment} \\
\midrule
\endhead
\bottomrule
\endlastfoot
Chapter 1: Introduction & 14 & tabularx \\
Chapter 2: Review of Literature & 14 & tabularx \\
Chapter 3: Research Methods & 16 & tabularx \\
Chapter 4: Data Analysis and Findings & 18 & tabularx \\
Chapter 5: Discussion and Recommendations & 10 & tabularx \\
\midrule
\textbf{Total (Chapters)} & \textbf{72} & \\
\end{xltabular}}

%-------------------------------------------------------------------------------
% Appendix A: Traceability
%-------------------------------------------------------------------------------
\section{Appendix A: Research Traceability Matrices (6 Tables)}
\label{sec:inv_app_a}

\noindent Table~\ref{tab:inv_app_a_tables} catalogues the six traceability matrices in Appendix~A.

\needspace{8\baselineskip}

\tablefontsize
\begin{xltabular}
{\textwidth}{@{} p{0.5cm} L L p{1cm} @{}}
\caption{Inventory of Tables in Appendix A: Traceability Matrices}
\label{tab:inv_app_a_tables} \\
\toprule
\thead{No.} & \thead{Label} & \thead{Caption} & \thead{Type} \\
\midrule
\endfirsthead
\endhead
\midrule
\multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot
1 & tab:trace\_t1 & Literature-to-Gap Traceability (T1) & LT \\
2 & tab:trace\_t2 & Gap to Research Objectives Traceability (T2) & LT \\
3 & tab:trace\_t3 & Objectives to Framework Components (T3) & LT \\
4 & tab:trace\_t4 & Existing Models vs.\ This Framework (T4) & LT \\
5 & tab:trace\_t5 & Research Questions to Framework Evidence (T5) & LT \\
6 & tab:trace\_t6 & Framework Outcome Traceability (T6) & LT \\
\end{xltabular}

\vspace{0.5em}\noindent\textit{Note.} LT = longtable environment. The six traceability matrices (T1--T6) provide end-to-end linkage from literature gaps through research questions to framework outcomes, addressing examiner concerns about research coherence.

%-------------------------------------------------------------------------------
% Appendices B--G: Domain-Specific Literature
%-------------------------------------------------------------------------------
\section{Appendices B--G: Domain-Specific Literature Reviews (6 Tables)}
\label{sec:inv_app_bg}

\noindent Table~\ref{tab:inv_app_bg_tables} catalogues the six domain-specific comparative analysis tables in Appendices~B--G.

\needspace{8\baselineskip}

\tablefontsize
\begin{xltabular}
{\textwidth}{@{} p{0.5cm} p{1cm} L L p{1cm} @{}}
\caption{Inventory of Tables in Appendices B--G: Domain-Specific Literature}
\label{tab:inv_app_bg_tables} \\
\toprule
\thead{No.} & \thead{App.} & \thead{Label} & \thead{Caption} & \thead{Type} \\
\midrule
\endfirsthead
\endhead
\midrule
\multicolumn{5}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot
1 & B & tab:asd\_comparison & Comparative Analysis of Recent ASD EEG Studies (2023--2025) & TX \\
2 & C & tab:pd\_comparison & Comparative Analysis of PD EEG Frameworks vs.\ Proposed ASD ensemble Design & TX \\
3 & D & tab:cancer\_comparison & Comparative Analysis of GAN-Based Hematological AI Frameworks & TX \\
4 & E & tab:stress\_comparison & Comparative Analysis of EEG Stress Detection Frameworks vs.\ Proposed RAG System & TX \\
5 & F & tab:agentic\_comparison & Comparative Analysis of Multi-Modal Medical AI vs.\ Agentic Disease Finder & TX \\
6 & G & \seqsplit{tab:wearable\_detail\_comparison} & Comparative Analysis of Wearable EEG Systems vs.\ Proposed MWSE-Framework & TX \\
\end{xltabular}

\vspace{0.5em}\noindent\textit{Note.} TX = tabularx environment. Each appendix (B--G) provides a single detailed comparative analysis table benchmarking this study's approach against recent domain-specific literature.

%-------------------------------------------------------------------------------
% Chapter 3: Supplementary Material (formerly Appendix H)
%-------------------------------------------------------------------------------
\section{Chapter 3 Supplementary Material: Research Methods (10 Tables)}
\label{sec:inv_app_h}

\noindent Table~\ref{tab:inv_app_h_tables} catalogues the ten supplementary tables supporting Chapter~3.

\needspace{8\baselineskip}

\tablefontsize
\begin{xltabular}
{\textwidth}{@{} p{0.5cm} L L p{1cm} @{}}
\caption{Inventory of Supplementary Tables in Chapter 3: Research Methods}
\label{tab:inv_app_h_tables} \\
\toprule
\thead{No.} & \thead{Label} & \thead{Caption} & \thead{Type} \\
\midrule
\endfirsthead
\endhead
\midrule
\multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot
1 & tab:kau\_asd\_eeg & KAU ASD-EEG Dataset Specifications & TX \\
2 & tab:physionet & PhysioNet PD Dataset Specifications & TX \\
3 & tab:deap & DEAP Dataset Specifications & TX \\
4 & tab:sam40 & SAM40 Dataset Specifications & TX \\
5 & tab:bci & BCI Competition IV 2a Specifications & TX \\
6 & tab:tcia & TCIA Dataset Specifications & TX \\
7 & tab:1dcnn & 1D-CNN Architecture & TX \\
8 & tab:cnnlstm & CNN-LSTM Architecture & TX \\
9 & tab:deepconvnet & DeepConvNet Architecture & TX \\
10 & tab:3dcnn & 3D-CNN Architecture for Cancer Radiomics & TX \\
\end{xltabular}

\vspace{0.5em}\noindent\textit{Note.} TX = tabularx environment. Tables 1--6 provide detailed dataset specifications (subjects, channels, sampling rates, classes). Tables 7--10 document four deep learning architectures with layer configurations.

%-------------------------------------------------------------------------------
% Chapter 4: Supplementary Material (formerly Appendix I)
%-------------------------------------------------------------------------------
\section{Chapter 4 Supplementary Material: Data Analysis (40 Tables)}
\label{sec:inv_app_i}

\noindent Table~\ref{tab:inv_app_i_tables} catalogues the 40 supplementary tables supporting Chapter~4, organised by thematic group.

\needspace{8\baselineskip}

\tablefontsize
\begin{xltabular}
{\textwidth}{@{} p{0.5cm} L L p{1cm} @{}}
\caption{Inventory of Supplementary Tables in Chapter 4: Data Analysis}
\label{tab:inv_app_i_tables} \\
\toprule
\thead{No.} & \thead{Label} & \thead{Caption} & \thead{Type} \\
\midrule
\endfirsthead
\endhead
\midrule
\multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot
\multicolumn{4}{l}{\textbf{Classification Results}} \\
\addlinespace
1 & tab:asd\_results & ASD Classification -- Complete Results & TX \\
2 & tab:pd\_results & Parkinson's Disease Classification -- Complete Results & TX \\
3 & tab:stress\_results & Stress Detection Classification -- Complete Results & TX \\
4 & tab:bci\_results & BCI Motor Imagery Classification -- Complete Results & TX \\
5 & tab:cancer\_results & Cancer Radiomics Classification -- Complete Results & TX \\
6 & tab:cv\_results & 10-Fold Cross-Validation Results (Best Models) & TX \\
7 & tab:statistical & Paired $t$-test Results: DL vs.\ Baseline & TX \\
\addlinespace
\multicolumn{4}{l}{\textbf{Quality Assurance Checklists}} \\
\addlinespace
8 & tab:checklist\_pretrain & Pre-Training Quality Assurance Checklist & TX \\
9 & tab:checklist\_training & During-Training Quality Assurance Checklist & TX \\
10 & tab:checklist\_posttrain & Post-Training Quality Assurance Checklist & TX \\
11 & tab:stat\_test\_guide & Statistical Test Selection Guide & TX \\
\addlinespace
\multicolumn{4}{l}{\textbf{Bias Detection and Mitigation}} \\
\addlinespace
12 & tab:bias\_detection & Bias Detection Techniques by Layer & TX \\
13 & tab:data\_mitigation & Data-Level Bias Mitigation & TX \\
14 & tab:model\_mitigation & Model-Level Bias Mitigation & TX \\
15 & tab:post\_mitigation & Post-Processing Bias Mitigation & TX \\
\addlinespace
\multicolumn{4}{l}{\textbf{Hallucination Prevention}} \\
\addlinespace
16 & tab:input\_validation & Input-Level Hallucination Prevention & TX \\
17 & tab:knowledge\_grounding & Knowledge Grounding Controls & TX \\
18 & tab:fact\_verification & Automated Fact Verification & TX \\
19 & tab:quality\_gates & Hallucination Quality Gates & TX \\
\addlinespace
\multicolumn{4}{l}{\textbf{Data Governance}} \\
\addlinespace
20 & tab:data\_classification & Data Classification Summary & TX \\
21 & tab:data\_retention & Data Retention by Type & TX \\
\addlinespace
\multicolumn{4}{l}{\textbf{Responsible AI Validation}} \\
\addlinespace
22 & tab:fairness\_validation & Fairness Validation Techniques & TX \\
23 & tab:privacy\_validation & Privacy Validation Techniques & TX \\
24 & tab:safety\_validation & Safety Validation Techniques & TX \\
25 & \seqsplit{tab:accountability\_validation} & Accountability Validation Techniques & TX \\
\addlinespace
\multicolumn{4}{l}{\textbf{Trust and Safety}} \\
\addlinespace
26 & tab:confidence\_signaling & Confidence Signaling & TX \\
27 & tab:trust\_boundaries & Trust Boundary Rules & TX \\
28 & tab:task\_boundaries & Explicit Task Boundaries & TX \\
29 & tab:risk\_levels & Risk Level Definitions & TX \\
30 & tab:explanation\_audiences & Audience-Specific Explanations & TX \\
\addlinespace
\multicolumn{4}{l}{\textbf{Guardrails and Governance}} \\
\addlinespace
31 & tab:input\_guardrails & Input Guardrail Rules & TX \\
32 & tab:output\_guardrails & Output Safety Filters & TX \\
33 & tab:raci\_appendix & RACI Responsibility Matrix & TX \\
34 & tab:robustness\_dimensions & Robustness Dimensions & TX \\
35 & tab:failure\_modes\_appendix & Failure Mode Handling & TX \\
36 & tab:portability & Portability Scope & TX \\
37 & tab:task\_responsibility & Task Responsibility Mapping & TX \\
\addlinespace
\multicolumn{4}{l}{\textbf{Deployment and Lifecycle}} \\
\addlinespace
38 & tab:eval\_results & Sample Model Evaluation Results & TX \\
39 & tab:deployment\_rules & Deployment Decision Rules & TX \\
40 & tab:lifecycle\_validation & Responsible-by-Design Lifecycle Validation & TX \\
\end{xltabular}

\vspace{0.5em}\noindent\textit{Note.} TX = tabularx environment. These 40 supplementary tables (now merged into Chapter~4) are organized into eight thematic groups spanning classification results, quality assurance, bias mitigation, hallucination prevention, data governance, responsible AI validation, trust boundaries, and deployment lifecycle.

%-------------------------------------------------------------------------------
% Chapter 5: Supplementary Material (formerly Appendix J)
%-------------------------------------------------------------------------------
\section{Chapter 5 Supplementary Material: Discussion (12 Tables)}
\label{sec:inv_app_j}

\noindent Table~\ref{tab:inv_app_j_tables} catalogues the 12 supplementary tables supporting Chapter~5.

\needspace{8\baselineskip}

\tablefontsize
\begin{xltabular}
{\textwidth}{@{} p{0.5cm} L L p{1cm} @{}}
\caption{Inventory of Supplementary Tables in Chapter 5: Discussion}
\label{tab:inv_app_j_tables} \\
\toprule
\thead{No.} & \thead{Label} & \thead{Caption} & \thead{Type} \\
\midrule
\endfirsthead
\endhead
\midrule
\multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot
1 & \seqsplit{tab:app\_j\_literature\_comparison} & Findings Compared with Prior Literature & TX \\
2 & \seqsplit{tab:app\_j\_gap\_closure} & Systematic Gap Closure Assessment & TX \\
3 & \seqsplit{tab:app\_j\_managerial\_implications} & Managerial Implications and Recommended Actions & TX \\
4 & \seqsplit{tab:app\_j\_roi\_model} & ROI Estimation Model for Framework Deployment & TX \\
5 & \seqsplit{tab:app\_j\_tco\_analysis} & Total Cost of Ownership: Unified Framework vs.\ Multi-Vendor (5-Year) & TX \\
6 & \seqsplit{tab:app\_j\_change\_impact} & Change Impact Analysis for Framework Adoption & TX \\
7 & \seqsplit{tab:app\_j\_vrin\_assessment} & VRIN Assessment of Framework Competitive Advantage & TX \\
8 & \seqsplit{tab:app\_j\_governance\_recommendations} & Governance and Policy Recommendations & TX \\
9 & \seqsplit{tab:app\_j\_clinical\_implications} & Clinical Practice Implications of Framework Deployment & TX \\
10 & \seqsplit{tab:app\_j\_regulatory\_pathways} & Regulatory Pathway Analysis for Clinical Deployment & TX \\
11 & \seqsplit{tab:app\_j\_scalability\_assessment} & Scalability Assessment & TX \\
12 & \seqsplit{tab:app\_j\_ch8\_quality} & Discussion Quality Assessment Matrix & TX \\
\end{xltabular}

\vspace{0.5em}\noindent\textit{Note.} TX = tabularx environment. These 12 supplementary tables (now merged into Chapter~5) provide the DBA-oriented analysis: ROI models, total cost of ownership, VRIN competitive advantage assessment, change impact analysis, and regulatory pathway mapping.

%-------------------------------------------------------------------------------
% Appendix H: Data Use Certificates (formerly Appendix K)
%-------------------------------------------------------------------------------
\section{Appendix H: Data Use Certificates (7 Tables)}
\label{sec:inv_app_k}

\noindent Table~\ref{tab:inv_app_k_tables} catalogues the seven data use certificate tables in Appendix~H.

\needspace{8\baselineskip}

\tablefontsize
\begin{xltabular}
{\textwidth}{@{} p{0.5cm} L L p{1cm} @{}}
\caption{Inventory of Tables in Appendix H: Data Use Certificates}
\label{tab:inv_app_k_tables} \\
\toprule
\thead{No.} & \thead{Label} & \thead{Caption} & \thead{Type} \\
\midrule
\endfirsthead
\endhead
\midrule
\multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot
1 & tab:data\_certificates & Data Use Certificate Summary for All Datasets & TX \\
2 & tab:cert\_kau\_asd\_eeg & Data Use Certificate: KAU ASD-EEG & TX \\
3 & tab:cert\_physionet & Data Use Certificate: PhysioNet & TX \\
4 & tab:cert\_deap & Data Use Certificate: DEAP & TX \\
5 & tab:cert\_sam40 & Data Use Certificate: SAM40 & TX \\
6 & tab:cert\_bci & Data Use Certificate: BCI Competition IV 2a & TX \\
7 & tab:cert\_tcia & Data Use Certificate: TCIA & TX \\
\end{xltabular}

\vspace{0.5em}\noindent\textit{Note.} TX = tabularx environment. Each data use certificate documents the dataset source, access date, license type, ethical compliance status, and permitted use conditions for the six publicly available datasets employed in this research.

%-------------------------------------------------------------------------------
% Grand Summary
%-------------------------------------------------------------------------------
\section{Grand Summary: All Tables}
\label{sec:inv_grand_summary}

\noindent Table~\ref{tab:inv_grand_total} reports the grand total of all tables across chapters and appendices.
\needspace{8\baselineskip}
{\tablestripes\tablefontsize
\begin{xltabular}{\textwidth}{@{} L C C @{}}
\caption{Grand Summary of All Tables in This Dissertation}\label{tab:inv_grand_total} \\
\toprule
\thead{Location} & \thead{Table Count} & \thead{Primary Environment} \\
\midrule
\endfirsthead
\multicolumn{3}{@{}l}{\textit{(\,Tab.~\ref{tab:inv_grand_total} continued from previous page\,)}} \\
\toprule
\thead{Location} & \thead{Table Count} & \thead{Primary Environment} \\
\midrule
\endhead
\bottomrule
\endlastfoot
Chapter 1: Introduction & 14 & tabularx \\
Chapter 2: Review of Literature & 14 & tabularx \\
Chapter 3: Research Methods (incl.\ supplementary) & 26 & tabularx \\
Chapter 4: Data Analysis and Findings (incl.\ supplementary) & 58 & tabularx \\
Chapter 5: Discussion and Recommendations (incl.\ supplementary) & 22 & tabularx \\
\addlinespace
Appendix A: Traceability Matrices & 6 & longtable \\
Appendices B--G: Domain Literature & 6 & tabularx \\
Appendix H: Data Certificates & 7 & tabularx \\
\midrule
\textbf{Grand Total} & \textbf{153} & \\
\end{xltabular}}

\vspace{0.5em}\noindent\textit{Note.} The 153 tables are distributed across five chapters (134 tables, 88\%, including supplementary material merged from former Appendices~H, I, J) and eight appendices (19 tables, 12\%). All tables use booktabs formatting (no vertical rules), navy-themed headers (\texttt{\textbackslash thead\{\}}), and alternating row shading (\texttt{\textbackslash tablestripes}).
