%% ============================================================================
%% Thematic cross-reference matrix
%% Single-page replacement for per-page compose-footers (§49 alternative)
%% Auto-generated 2026-05-27
%% ============================================================================

\clearpage
\subsection{Thematic Cross-Reference Matrix --- Related Tables Grouped by Topic}
\label{sec:thematic_xref_matrix}

\noindent\emph{Single-page thematic grouping of the 100+ dedicated-page tables added in this Ch.~3 architectural expansion. Each row identifies one theme and lists the 4--7 tables most closely related; this single matrix replaces per-page compose-footers. Use this matrix to navigate clusters of related architecture / analysis / governance topics.}

\paragraph{Thematic Cross-Reference Matrix.}


\noindent This table lists each \textit{theme} with its related tables (4--7 per theme), so examiners can trace what was assessed and what evidence supports each row.



\noindent This table lists each \textit{theme} with its related tables (4--7 per theme), so examiners can trace what was assessed and what evidence supports each row.


\noindent This table lists each \textit{theme} with its related tables (4--7 per theme), so examiners can trace what was assessed and what evidence supports each row.



{\tablestripes\tablefontsize
\needspace{10\baselineskip}
\begin{xltabular}{\textwidth}{@{} >{\raggedright\arraybackslash}p{7.5cm} p{6.3cm} @{}}
\caption[Thematic Cross-Reference Matrix]{Thematic Cross-Reference Matrix --- 18 Themes Linking 100+ Dedicated-Page Tables.}\label{tab:thematic_xref_matrix} \\
\toprule
\thead{Theme} & \thead{Related tables (4--7 per theme)} \\
\midrule
\endfirsthead
\endhead
\bottomrule
\endfoot
1. Pipeline architecture (23 steps) & Tables \ref{tab:asd_23step_expanded}, \ref{tab:pipeline_sample_data}, \ref{tab:pipeline_step_objective}, \ref{tab:pipeline_step_governance} \\
2. Pipeline phase detail (per-phase) & \ref{tab:preproc_detail}, \ref{tab:conversion_detail}, \ref{tab:fft_detail}, \ref{tab:swt_detail}, \ref{tab:image_conversion} \\
3. Sample data (KAU autism cohort) & \ref{tab:pipeline_sample_data}, \ref{tab:sec_data_sample}, \ref{tab:healthy_vs_asd_window}, \ref{tab:wavelength_freq_healthy_vs_asd} \\
4. EEG technical specifications & \ref{tab:primary_eeg_technical}, \ref{tab:channels_10_20_system}, \ref{tab:brain_regions_list}, \ref{tab:wavelength_freq_healthy_vs_asd}, \ref{tab:fft_detail}, \ref{tab:swt_detail} \\
5. Behavioural assessment instruments & \ref{tab:primary_behavioral_assessments}, \ref{tab:primary_clinical_data_items}, \ref{tab:b2c_b2b_assessment_crosswalk}, \ref{tab:severity_tiers} \\
6. Population + inclusion / exclusion & \ref{tab:primary_pediatric_population}, \ref{tab:primary_inclusion_exclusion}, \ref{tab:primary_not_required_identifiers}, \ref{tab:severity_tiers}, \ref{tab:asd_impact_per_domain} \\
7. Data quality + preprocessing & \ref{tab:primary_analysis_data_quality}, \ref{tab:primary_analysis_preprocessing}, \ref{tab:brutal_primary_preprocess_deepdive}, \ref{tab:eda_plan}, \ref{tab:graph_projection} \\
8. Feature engineering + selection & \ref{tab:brutal_primary_feature_eng}, \ref{tab:brutal_primary_normalization}, \ref{tab:image_conversion}, \ref{tab:brutal_1d_2d_conversion_per_phase} \\
9. Model architecture + training & \ref{tab:model_architecture_detail}, \ref{tab:sec_data_models}, \ref{tab:accuracy_per_model}, \ref{tab:sec_data_accuracy}, \ref{tab:benchmarking_comparison} \\
10. Analysis plan + statistical tests & \ref{tab:primary_analysis_sap_per_hypothesis}, \ref{tab:statistical_analysis_list}, \ref{tab:sensitivity_analysis_list}, \ref{tab:subjective_analysis_list}, \ref{tab:monte_carlo_vs_bootstrap} \\
11. Subgroup + fairness + bias & \ref{tab:primary_analysis_subgroup_fairness}, \ref{tab:brutal_primary_bias_inventory}, \ref{tab:brutal_balance_handling}, \ref{tab:primary_analysis_validity} \\
12. Longitudinal + missing data & \ref{tab:primary_analysis_longitudinal}, \ref{tab:primary_analysis_missing_data}, \ref{tab:primary_analysis_reliability}, \ref{tab:brutal_analysis_flow} \\
13. RAG + LLM + retrieval & \ref{tab:vector_db_qdrant}, \ref{tab:graph_db_design}, \ref{tab:pii_index_retrieval_chunking}, \ref{tab:output_eval_ragas}, \ref{tab:cron_llm_cache} \\
14. Per-phase AI dimensions (XAI/RAI/Sec/Gov/HITL) & \ref{tab:tools_per_stage}, \ref{tab:xai_per_stage}, \ref{tab:rai_per_stage}, \ref{tab:secure_ai_per_stage}, \ref{tab:governance_per_stage}, \ref{tab:sec_data_ai_dimensions_per_phase} \\
15. RGAIG + SMART frameworks per phase & \ref{tab:sec_data_rgaig}, \ref{tab:sec_data_smart}, \ref{tab:rgaig_per_phase}, \ref{tab:smart_per_phase} \\
16. ISO 42001 + healthcare ISO + audit & \ref{tab:per_phase_library_kpi}, \ref{tab:per_phase_ipo_benchmark}, \ref{tab:per_phase_iso_42001}, \ref{tab:iso_audit_runbook} \\
17. Secondary data + AS-IS + TO-BE & \ref{tab:sec_data_as_is}, \ref{tab:sec_data_challenges}, \ref{tab:sec_data_journey_lifecycle}, \ref{tab:sec_data_to_be}, \ref{tab:as_is_process_detail}, \ref{tab:as_is_challenges}, \ref{tab:to_be_emotiv_iot} \\
18. Database schema + reporting & \ref{tab:brutal_db_design}, \ref{tab:brutal_secondary_db_schema}, \ref{tab:master_db_schema}, \ref{tab:survey_report_save_schema}, \ref{tab:data_flow_reporting_flow}, \ref{tab:sec_data_as_is_reports} \\
\end{xltabular}}
\vspace{0.3em}\noindent\textit{Note.} Themes are designed for reader convenience: pick a theme, follow the 4--7 cross-references to engage related architecture / analysis / governance topics without searching the full 105-table index (Table~\ref{tab:crossref_index_new}). The matrix replaces per-page compose-footers with one consolidated reference; the per-table index remains available for label-driven lookup.
