%% Appendix S — Glossary of Acronyms and Key Terms
\chapter{Glossary of Acronyms and Key Terms}


\noindent\textbf{Purpose.} This appendix is provided to support transparency, traceability, reproducibility, and examination defensibility. The material contained herein supplements, but does not replace, the primary findings reported in Chapters~1--5. No major conclusions rely exclusively on appendix content.

\label{chap:appendix_s_glossary}

\noindent Alphabetic reference for every acronym and key term used in this dissertation. First-use expansions in chapter bodies cross-reference this appendix.

\noindent Table~\ref{tab:glossary_full} below lists every acronym + key term used in this dissertation, alphabetised, with one-line definition.

{\tablestripes\tablefontsize
\needspace{20\baselineskip}
\begin{xltabular}{\textwidth}{@{} >{\raggedright\arraybackslash}p{2.6cm} L @{}}
\caption[Glossary of Acronyms and Key Terms]{Glossary of Acronyms and Key Terms. Alphabetic; first-use in chapter body cross-references this entry.}\label{tab:glossary_full} \\
\toprule
\thead{Term / Acronym} & \thead{Definition} \\
\midrule
\endfirsthead
\endhead
\bottomrule
\endfoot
ABIDE-II & Autism Brain Imaging Data Exchange (second release) --- public multi-site neuroimaging + behavioural dataset for ASD research. \\
ACC & Classification accuracy --- fraction of correct predictions on a held-out test set. \\
ADOS-2 & Autism Diagnostic Observation Schedule (second edition) --- standardised behavioural assessment for ASD diagnosis. \\
AES-256 & Advanced Encryption Standard with 256-bit key --- symmetric block cipher for data-at-rest encryption. \\
AI & Artificial Intelligence. \\
AI Act & European Union Artificial Intelligence Act (Regulation 2024/1689) governing high-risk AI systems. \\
ASD & Autism Spectrum Disorder. \\
AUC & Area Under the Receiver Operating Characteristic Curve. \\
B2B & Business-to-Business --- in this thesis, the clinician-facing institutional channel (hospital, clinic). \\
B2C & Business-to-Consumer --- in this thesis, the caregiver-facing at-home channel. \\
BCI & Brain--Computer Interface. \\
BDF & BioSemi Data Format --- 24-bit raw EEG file format. \\
BIDS & Brain Imaging Data Structure --- community standard for organising neuroimaging datasets. \\
CARS-2 & Childhood Autism Rating Scale (second edition) --- clinician-administered ASD severity rating. \\
CI & Confidence Interval. \\
CNN & Convolutional Neural Network. \\
DBA & Doctor of Business Administration. \\
DI & Disparate Impact --- fairness metric; ratio of favourable outcomes between protected and reference group; target $\geq$ 0.80 per US EEOC 4/5ths rule. \\
DPDP & Digital Personal Data Protection (India Act 2023). \\
EDF & European Data Format --- 16-bit raw EEG / polysomnography file format. \\
EEG & Electroencephalography. \\
Emotiv & Brand name for consumer-grade wearable EEG headsets (Insight, EPOC X, EPOC Flex) used in this thesis. \\
EU AI Act & See AI Act. \\
F1 & F1-score --- harmonic mean of precision and recall. \\
FIF & Functional Image Format --- MNE-Python native EEG / MEG file format. \\
GDPR & General Data Protection Regulation (EU Regulation 2016/679). \\
HIPAA & Health Insurance Portability and Accountability Act (US, 1996). \\
HITL & Human-in-the-Loop --- design pattern where a human reviewer must approve / reject AI-generated outputs before they reach the end user. \\
HTMT & Heterotrait-Monotrait ratio --- SEM discriminant validity metric; target $<$ 0.85. \\
ICA & Independent Component Analysis --- blind-source-separation algorithm used to remove EEG artifacts. \\
IEC 62304 & International Electrotechnical Commission standard for medical-device software life-cycle processes. \\
IRB / IEC & Institutional Review Board / Institutional Ethics Committee --- research ethics approval body. \\
ISO 13485 & International standard for medical-device quality-management systems. \\
ISO 14971 & International standard for medical-device risk management. \\
ISO 42001 & International standard for AI management systems (published 2023). \\
ISO/IEC 27001 & International standard for information-security management systems. \\
JSON-LD & JavaScript Object Notation for Linked Data --- semantic-web data interchange format. \\
KAU & King Abdulaziz University (Saudi Arabia) --- primary clinical-data partner for this thesis. \\
KPI & Key Performance Indicator. \\
KS & Kolmogorov--Smirnov test --- non-parametric distribution-comparison statistic. \\
LIME & Local Interpretable Model-agnostic Explanations --- per-prediction XAI method. \\
LOSO & Leave-One-Subject-Out cross-validation. \\
MAE & Mean Absolute Error. \\
MAPE & Mean Absolute Percentage Error. \\
MCP & Model Context Protocol --- emerging open standard for tool-call audit in agentic AI systems. \\
MNE-Python & Open-source Python library for processing M/EEG data. \\
MRR & Mean Reciprocal Rank --- ranking-evaluation metric (RAG retrieval). \\
nDCG & Normalised Discounted Cumulative Gain --- ranking-evaluation metric. \\
NIST RMF & National Institute of Standards and Technology (US) AI Risk Management Framework. \\
OSF & Open Science Framework --- public registry for study pre-registrations. \\
PD-1 & Primary Data --- caregiver SEM survey (Phase 1). \\
PD-2 & Primary Data --- clinician Delphi panel (Phase 1). \\
PD-3 & Primary Data --- caregiver usability focus group (Phase 2). \\
PD-4 & Primary Data --- clinician interviews (Phase 2). \\
PD-5 & Primary Data --- regulator stakeholder interviews (Phase 2). \\
PII & Personally Identifiable Information. \\
PLS-SEM & Partial Least Squares Structural Equation Modeling. \\
PRISMA & Preferred Reporting Items for Systematic Reviews and Meta-Analyses (2020 update). \\
PSI & Population Stability Index --- distribution-drift metric; target $<$ 0.20. \\
RAG & Retrieval-Augmented Generation --- LLM design pattern that grounds responses in retrieved source chunks. \\
Ragas & Open-source RAG-quality evaluation framework; key metric is Faithfulness (target $\geq$ 0.85). \\
RAI & Responsible AI. \\
RGAIG & Responsible Generative AI Governance --- the 7-layer governance framework introduced in this thesis. \\
RMSE & Root Mean Square Error. \\
ROC & Receiver Operating Characteristic. \\
RQ & Research Question. \\
SD-A through SD-E & Secondary Data --- 5 sources: KAU clinical EEG, ABIDE-II ASD imaging, OASIS-3 control, KAU behavioural records, hospital EHR extracts. \\
SEM & Structural Equation Modeling. \\
SHAP & SHapley Additive exPlanations --- per-prediction XAI method based on cooperative game theory. \\
SIEM & Security Information and Event Management --- enterprise log aggregation + alert platform. \\
SOC2 & Service Organization Control 2 (AICPA) --- audit framework for service-organisation security + availability + confidentiality. \\
SQI & Signal Quality Index --- per-EEG-record quality score; minimum-acceptable threshold 0.70 in this thesis. \\
SUS & System Usability Scale --- standard 10-item usability questionnaire; industry-baseline mean 68. \\
SWT & Stationary Wavelet Transform. \\
TAM & Technology Acceptance Model. \\
TikZ & LaTeX vector-graphics package used for all flowcharts and diagrams in this dissertation. \\
UTAUT & Unified Theory of Acceptance and Use of Technology. \\
ViT & Vision Transformer --- deep-learning architecture applied to image-converted EEG spectrograms. \\
WHO & World Health Organization. \\
XAI & Explainable AI. \\
\end{xltabular}}
\vspace{0.3em}\noindent\textit{Note.} Glossary covers every acronym used $\geq$ 3 times across the dissertation. Each entry contains $\leq$ 2 sentences (definition + key threshold or example). For deeper background see the appendix or chapter cited.
